But I can't preregister my research: Improving the reproducibility and transparency of ecology and conservation with adaptive preregistration for model-based research

### 2025-03-03 _analysis/ms.qmd
Finish update methods section

@@

>>>>

## Developing an Adaptive Preregistration Methodology

@@

## Evaluating and Refining Adaptive Preregistration with a Case Study

We preregistered a real-world model-based research problem as a case-study for evaluating and testing the Preregistration Template and proposed Adaptive Preregistration methodology. The case study analysed the effectiveness of environmental flows on maintaining riparian vegetation condition in Victoria, Australia [@Tonkin2020]. We captured the case-study researchers’ feedback about the Preregistration Template and Adaptive Preregistration methodology using the version-control and collaborative project management features of git and GitHub [@BenBondLamberty:2018by; @Blischak:2016kr; @braga2023]. We used these tools for documenting both the analytic decisions of the researcher, and for using the preregistration process itself to ‘live-develop’ the template. For example, if it turned out that we had missed an important item, or the order and structure of the template needed to change in the process of completing the preregistration, the suggested change and its justification would be both recorded in GitHub. We also conducted follow-up semi-structured interviews to capture more detailed reflections of the case-study researchers.
